FinalManuscript_DISCS_UG

### 2018-06-26 parts/01_introduction_01contextofstudy.tex

Digital data privacy and security is a growing concern in various fields, such as  cloud computing \cite{potey_homomorphic_2016}, health information systems \cite{kester_cryptographic_2015}, and video surveillance \cite{upmanyu_efficient_2009}. To meet these needs, various cryptosystems have been developed. A cryptosystem is a system which operates on plaintexts, ciphertexts and keys. a cryptosystem also has an encryption algorithm, which maps a plaintext to a ciphertext, and a decryption algorithm, which maps a ciphertext to a plaintext, given an appropiate key \cite{bauer_cryptosystem_2005}. The encryption and decryption algorithms are chosen such that the plaintext cannot easily be recovered from the ciphertext without knowledge of the key. This allows data to be securely transmitted over an insecure channel:  and thus much research has been done on the development and application of various cryptosystems.

>>>>

Digital data privacy and security is a growing concern in various fields, such as cloud computing \cite{potey_homomorphic_2016}, health information systems \cite{kester_cryptographic_2015}, and video surveillance \cite{upmanyu_efficient_2009}. To meet these needs, various cryptosystems have been developed. A cryptosystem is a system which operates on plaintexts, ciphertexts and keys. a cryptosystem also has an encryption algorithm, which maps a plaintext to a ciphertext, and a decryption algorithm, which maps a ciphertext to a plaintext, given an appropriate key \cite{bauer_cryptosystem_2005}. The encryption and decryption algorithms are chosen such that the plaintext cannot easily be recovered from the ciphertext without knowledge of the key. This allows data to be securely transmitted over an insecure channel:  and thus much research has been done on the development and application of various cryptosystems.
